Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-02-06 ForegroundSimulations/ms.tex
Update Introduction section
From c14f775 (master):
=====================

In ms.tex,

(*) Update Introduction section

\shorttitle{Characterization of Beam Chromaticity in EoR Power Spectra Measurements}
\shortauthors{Thyagarajan et~al.}

@@

When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization. The extreme dynamic range required to subtract foregrounds precisely demands high precision modeling of foregrounds as observed by modern wide-field instruments \citep{,thy15a,thy15b}.

@@

\section{Chromaticity of Power Pattern}

@@

\subsection{Directional Chromaticity of Power Pattern}

@@

\subsection{Effect on Delay Power Spectrum}

@@

Fig.~\ref{fig:asm-dps-beam-chromaticity} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern. In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively. The vertical gray lines denote the horizon limits for a 14.6~m antenna spacing. The full band delay power spectra of the foregrounds measured on a 14.6~m antenna spacing oriented eastward is shown in the top left panel. A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity. For instance, the spillover from foreground delay power spectrum obtained with simulated dish pattern extends out to $k_\parallel \approx \pm 0.14\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it extends out to $k_\parallel \approx \pm 0.08\,h$~Mpc$^{-1}$, while the achromatic beam extends it only out to $k_\parallel \approx \pm 0.05\,h$~Mpc$^{-1}$. Thus an increase in chromaticity extends the foreground spillover into higher $k_\parallel$-modes making them inaccessible for EoR H{\sc i} signal detection.

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{asm_beam_chromaticity_subband_150_MHz.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra. }
\label{fig:asm-dps-beam-chromaticity}
\end{figure*}

@@

\subsection{Constraints on Reflections between Antennas}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast.eps}
\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
\label{fig:fg-reflections}
\end{figure*}

>>>>

\shorttitle{Effects of Beam Chromaticity in EoR Power Spectra Measurements}
\shortauthors{Thyagarajan et~al.}

@@

When expressed in the coordinate system of power spectrum measurements described by the three-dimensional wavenumber ($k$), the foreground emission is restricted to a wedge-shaped region commonly referred to as the {\it foreground wedge} \citep{bow09,liu09,liu14a,liu14b,dat10,liu11,gho12,mor12,par12b,tro12,ved12,dil13,pob13,thy13,dil14} whereas the EoR signal has spherical symmetry due to its isotropy which appears elongated along line of sight $k$ modes due to peculiar velocity effects when dominated by matter density perturbations during early stages of reionization.

The extreme dynamic range required to subtract foregrounds precisely demands high precision modeling of foregrounds as observed by modern wide-field instruments \citep{thy15a,thy15b}. Their studies of effects of wide-field measurements of EoR power spectra have demonstrated the {\it pitchfork} effect wherein foreshortening of baselines causes a prominent enhancement of foreground power near the horizon limits of the {\it foreground wedge} as well in the contamination beyond. In this paper, we explore yet another phenomenon that inherently extends foreground power beyond the {\it wedge}, namely, that arising from the chromaticity of the antenna power pattern. % We specifically use the current design of 14~m dish of HERA as an example in our study.

This paper is organized as follows. \S\ref{sec:HERA} introduces the HERA instrument. A brief summary of the delay spectrum technique used extensively in this analysis and the recently confirmed {\it pitchfork} effect are presented in \S\ref{sec:delay-spectrum}. \S\ref{sec:sim} describes foreground simulations including antenna beam pattern and all-sky foreground models. \S\ref{sec:beam-chromaticity} investigates the effects of chromaticity of antenna beam on the resulting delay power spectrum and the cosmologically motivated constraints it places on dish reflectometry. Our findings are summarized in \S\ref{sec:summary}.

@@

\section{Chromaticity of Power Pattern}\label{sec:beam-chromaticity}

@@

\subsection{Directional Chromaticity of Power Pattern}\label{sec:directional-chromaticity}

@@

\subsection{Effect on Delay Power Spectrum}\label{sec:chromaticity-delay-spectrum}

@@

Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines} shows the delay power spectra of foregrounds obtained with the aforementioned models for power pattern. In all these panels, power spectra obtained with achromatic, {\it Airy} disk and simulated disk are shown in black, red, and blue respectively. The vertical gray lines denote the horizon limits for a 14.6~m antenna spacing. The full band delay power spectra of the foregrounds measured on a 14.6~m antenna spacing oriented eastward is shown in the top left panel. A clear trend of broadening of spillover-wings outside the horizon limits is seen with increasing chromaticity. For instance, the spillover from foreground delay power spectrum obtained with simulated dish pattern extends out to $k_\parallel \approx \pm 0.14\,h$~Mpc$^{-1}$, with the {\it Airy} pattern it extends out to $k_\parallel \approx \pm 0.08\,h$~Mpc$^{-1}$, while the achromatic beam extends it only out to $k_\parallel \approx \pm 0.05\,h$~Mpc$^{-1}$. Thus an increase in chromaticity extends the foreground spillover into higher $k_\parallel$-modes making them inaccessible for EoR H{\sc i} signal detection.

@@

% \begin{figure*}[htb]
% \centering
% \includegraphics[width=\linewidth]{asm_beam_chromaticity_bl2_LST_3.96_hrs_subband_150.0_MHz.eps}
% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 14.6~m baseline.}
% \label{fig:asm-dps-beam-chromaticity-14.6m-baseline}
% \end{figure*}

% \begin{figure*}[htb]
% \centering
% \includegraphics[width=\linewidth]{asm_beam_chromaticity_bl8_LST_3.96_hrs_subband_150.0_MHz.eps}
% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for a 29.2~m baseline.}
% \label{fig:asm-dps-beam-chromaticity-29.2m-baseline}
% \end{figure*}

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{asm_foreground_eor_beam_chromaticity_fullband.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra for different baselines.}
\label{fig:asm-dps-beam-chromaticity-baselines}
\end{figure*}

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_150.0_MHz_subband.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 150~MHz subband for different baseline lengths.}
\label{fig:asm-dps-beam-chromaticity-baselines-150-subband}
\end{figure*}

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband.eps}
\caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
\label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
\end{figure*}

@@

\subsection{Constraints on Reflections between Antennas}\label{sec:reflectometry}

@@

\begin{figure*}[htb]
\centering
\includegraphics[width=\linewidth]{spec_on_foreground_reflected_power_21cmfast_14.6m_150.0_MHz_subband_v2.eps}
\caption{Attenuation of foreground power (in dB) from antenna-to-antenna reflections required to keep the reflected foreground power below EoR H{\sc i} signal power.}
\label{fig:fg-reflections}
\end{figure*}
